Test data

### 2022-07-21 Shiny/Test/Test data.Rmd
Public grants KPI, proposed private/public KPI.

>>>>

### Public grants growth
```{r}
kreft_excel |> 
  transmute(
    growth = revenue_public_grants[1] / revenue_public_grants[2] * 100
  ) |> 
  pull() |> 
  first()
```

### Private/public
```{r}
kreft_excel |> 
  transmute(
    proportion = revenue_private_contributions / revenue_public_grants * 100
  ) |> 
  pull() |> 
  first()
```
